Spatiotemporal Data Classification

### 2017-12-28 Report/BigDataHomework1.tex
changes in report: main.py, output folders, add references

    In the Main.py file, it is required to provide the path to the output folder as well as the input file with the training data. Afterwards, three folders are created to keep the images with the trips' visualizations for questions 1c, 2a1 and 2a2 and then the functions implementing the project's tasks are called.

@@

	\subsection{Question C}
	This task is implemented in the file DataVisualization.py and the created output is stored in the folder Question1C. The requirement is to visualize five of the given train trips. For this purporse, a new trips list is creating containing five trips, excluding all trips with null journey\_id. Afterwards, the data\_visualization function is called, and a points list is created having two tuples with all the longitudes and latitudes(function idx\_to\_lonlat in the utils.py).

@@

	\subsection{Question A1}
	For this part a test file is given (test\_set\_a1.csv) containing additional trips. For each of these trips, the k nearest neighbours are targeted (in this exercise k=5) and an image file is produced, showing all six trips (the test trip and the trips from the training file) on six different maps. Under each map, the neighbour index, the journey\_id, the dynamic time warping and the time needed to process the neighbours of this test trip in millisec.

@@

	\newpage
	\addcontentsline{toc}{section}{References}
	\begin{thebibliography}{30}
		\bibitem{first} 
    \end{thebibliography}

>>>>

    In the Main.py file, it is required to provide the path to the input folder (containing the training and test files) and the output folder where all results will be stored. In this folder an additional directory is created, in order to keep all maps extracted from this application. There are two ways in order to run this project, either add these folders in the edit configurations choice from the menu, or use the run.sh in order to provide these args. Finally, the dependencies are checked and the folders and files are prepared before starting to run the application.

@@

	\subsection{Question C}
	This task is implemented in the file DataVisualization.py and the created output is stored in the output folder in the gmplots directory. The requirement is to visualize five of the given train trips. For this purporse, a new trips list is creating containing five trips, excluding all trips with null journey\_id. Afterwards, the data\_visualization function is called, and a points list is created having two tuples with all the longitudes and latitudes(function idx\_to\_lonlat in the utils.py).

@@

	\subsection{Question A1}
	For this part a test file is given (test\_set\_a1.csv, included in the input folder) containing additional trips. For each of these trips, the k nearest neighbours are targeted (in this exercise k=5) and an image file is produced, showing all six trips (the test trip and the trips from the training file) on six different maps. Under each map, the neighbour index, the journey\_id, the dynamic time warping and the time needed to process the neighbours of this test trip in millisec.

@@

	\newpage
	\addcontentsline{toc}{section}{References}
	\begin{thebibliography}{30}
		\bibitem{knn}SciKit Learn: Nearest Neighbors \\
		 \url{http://scikit-learn.org/stable/modules/neighbors.html}
		 \bibitem{logreg} SciKit Learn: Logistic Regression \\
		 \url{http://scikit-learn.org/stable/modules/linear_model.html#logistic-regression}
		 \bibitem{ranfor} SciKit Learn: Random Forest \\
		 \url{http://scikit-learn.org/stable/modules/generated/sklearn.ensemble.RandomForestClassifier.html#sklearn.ensemble.RandomForestClassifier}
		 \bibitem{accuracy} SciKit Learn: Accuracy \\
		 \url{http://scikit-learn.org/stable/modules/generated/sklearn.metrics.accuracy_score.html#sklearn.metrics.accuracy_score}
		 \bibitem{knn2}A Complete Guide to K-Nearest-Neighbors with Applications in Python and R \\
		 \url{https://kevinzakka.github.io/2016/07/13/k-nearest-neighbor/}
		 \bibitem{dwt} Dynamic time warping \\
		 \url{https://en.wikipedia.org/wiki/Dynamic_time_warping}
		 \bibitem{lcss} Longest common subsequence problem \\
		 \url{https://en.wikipedia.org/wiki/Longest_common_subsequence_problem}
    \end{thebibliography}
